cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-08 paper-cardinalR.Rmd
Started fixing captions with code in PDF

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $4\\text{-}D$ `orglinearbranches` data. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.", fig.width=12, fig.height=4, fig.pos="H", fig.alt="Three $2\\text{-}D$ projections of the $4\\text{-}D$ orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.", fig.pos="!ht"}

@@

spherefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr 1fr;
    gap: 0px;
    align-items: start;
    justify-items: center;
    margin: 0;
    padding: 0;",
    circle_lang, curvycycle_lang, clusteredspheres_lang),
  #widths=c(3,3,3),
  device = "xs"
)

@@

spherefig
```

>>>>

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $4\\text{-}D$ data generated using \\texttt{gen\\_orgcurvybranches}. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.", fig.width=12, fig.height=4, fig.pos="H", fig.alt="Three $2\\text{-}D$ projections of the $4\\text{-}D$ orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.", fig.pos="!ht"}

@@

spherefig <- bscols(
  htmltools::div(
    style = "
      display: grid; 
      grid-template-columns: repeat(3, 1fr);
      gap: 0;
      width: 100%;
      margin: 0 auto;
      max-width: 100%;
    ",
    circle_lang,
    curvycycle_lang,
    clusteredspheres_lang
  ),
  device = "xs"
)

@@

htmltools::div(
  style = "max-width: 100%; width: 100%; margin: 0 auto;",
  spherefig
)

### 2025-12-08 paper-cardinalR.tex
Started fixing captions with code in PDF

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three $2\text{-}D$ projections of the $4\text{-}D$ orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.}]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from the $4\text{-}D$ `orglinearbranches` data. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.}\label{fig:branch-proj}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three $2\text{-}D$ projections of the $4\text{-}D$ orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.}]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from the $4\text{-}D$ data generated using \texttt{gen\_orgcurvybranches}. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.}\label{fig:branch-proj}
\end{figure}
